Aural skills and the underlying structure of music \\ \large An audio-based approach to Music Structure Analysis (MSA) using musically motivated deep learning

### 2023-02-16 introduction/introduction.tex
Updates from Overleaf

This master thesis investigates the interrelationship between music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition. It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, aural skills, and the underlying musical structure in musical composition. Musical elements, including melody, harmony, rhythm, and form, constitute music structure analysis.

Aural skills encompass perceptual and cognitive abilities, enabling individuals to comprehend musical works through listening. These skills encompass the ability to differentiate musical elements, comprehend relationships between them, and discern the structure of a musical composition.

The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.

This master thesis investigates the interplay between music structure analysis, aural skills, and the underlying musical structure through a comprehensive analysis of musical works from diverse styles and genres. By utilizing computational techniques from Music Information Retrieval (MIR) and incorporating a musicological perspective to contextualize the findings, this thesis aspires to offer a fresh and insightful examination of these components of musical composition and further our understanding of their relationships.

@@

@@

\begin{itemize}
\item Introduction
  \begin{itemize}
  \item Purpose
  \item Methodology
  \item Scope
  \end{itemize}
\item Main Body
  \begin{itemize}
  \item Section 1
  \item Section 2
  \item Section 3
  \end{itemize}
\item Conclusion
  \begin{itemize}
  \item Summary
  \item Recommendations
  \end{itemize}
\item References
  \begin{itemize}
  \item Sources Cited
  \end{itemize}
\end{itemize}

>>>>

Music is a complex and fascinating art form that has been studied by scholars and musicians for centuries. Music theory plays a crucial role in understanding the underlying principles of how music is organized and composed, and analyzing the structure of music is a challenging task.

Recently, the field of Music Structure Analysis (MSA) has emerged as a subfield of Music Information Retrieval (MIR), aiming to develop computational methods to analyze the structure of music. This master thesis investigates the relationship between MSA, aural skills, and the underlying musical structure in musical composition.

The thesis explores the musical elements that constitute music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition. It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, including melody, harmony, rhythm, and form. Aural skills involve perceptual and cognitive abilities that enable individuals to comprehend musical works through listening. The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.

This thesis provides a comprehensive analysis of musical works from diverse styles and genres, utilizing computational techniques from MIR and incorporating a musicological perspective to contextualize the findings.

The goal of this research is to offer fresh insights into these components of musical composition and advance our understanding of their relationships.

@@

Music is a complex and multi-faceted phenomenon, and implementing a model that mimics human aural music skills is challenging. However, using the latest deep learning techniques, we aim to build a model that achieves good results for a specific task in the domain of music.

@@

\begin{itemize}
\item Chapter 1
  \begin{itemize}
  \item Purpose
  \item Methodology
  \item Scope
  \end{itemize}
\item Chapter 2
  \begin{itemize}
  \item Section 1
  \item Section 2
  \item Section 3
  \end{itemize}
\item Chapter 3
  \begin{itemize}
  \item Summary
  \item Recommendations
  \end{itemize}
\item References
  \begin{itemize}
  \item Sources Cited
  \end{itemize}
\end{itemize}

### 2023-02-16 music analysis/MSA.tex
Updates from Overleaf

The musical structure analysis (MSA) challenges the definition due to subjectivity, ambiguity\footnote{Perception and interpretation of musical structure can vary widely between individuals and depend on factors such as personal background, cultural context, and individual preferences. This is due to the complex interplay between individual differences in perception and interpretation and how the auditory system processes sound. These factors highlight the importance of considering individual and cultural context in analyzing and interpreting musical structure.}, and data scarcity. A flat structural analysis of an audio signal consists of a set of contiguous, non-overlapping, and labeled time intervals that span the entire duration of the audio signal. Given a musical recording of T audio samples, a flat segmentation is defined by a set of segment boundaries B, a set of k unique labels Y, and a mapping of segment starting points to labels S. This leads to the label assignment L, which assigns a label to each time point. The segment boundaries are usually sampled at a rate of 10 Hz to achieve a balance between resolution and computational efficiency.

>>>>

MSA challenges its definition due to subjectivity, ambiguity\footnote{Perception and interpretation of musical structure can vary widely between individuals and depend on factors such as personal background, cultural context, and individual preferences. This is due to the complex interplay between individual differences in perception and interpretation and how the auditory system processes sound. These factors highlight the importance of considering individual and cultural context in analyzing and interpreting musical structure.}, and data scarcity. A flat structural analysis of an audio signal consists of a set of contiguous, non-overlapping, and labeled time intervals that span the entire duration of the audio signal. Given a musical recording of T audio samples, a flat segmentation is defined by a set of segment boundaries B, a set of k unique labels Y, and a mapping of segment starting points to labels S. This leads to the label assignment L, which assigns a label to each time point. The segment boundaries are usually sampled at a rate of 10 Hz to achieve a balance between resolution and computational efficiency.
